Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-29 paper/ICPC19/icpc19.tex
new update

@@

\begin{figure}[H]
 	\centering 	\includegraphics[width=0.45\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with 1/10 guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}

@@

Regarding security commits results, we observe that maintainability decreases in 40.20\% (244), increases in 29.33\% (178) and stays the same in 30.5\% (185) of the cases after security refactorings being applyed. The resulting p-value of the Wilcoxon signed-rank test is $1.21$x$10^{-10}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{security refactorings have a negative impact in the maintainability of open-source software}.

@@

@@

>>>>

\usepackage{xfrac}

@@

\begin{figure}[H]
 	\centering 	\includegraphics[width=0.45\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with $\sfrac{1}{10}$ guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}

@@

Regarding security commits results, we observe that maintainability decreases in 40.20\% (244), increases in 29.33\% (178) and stays the same in 30.5\% (185) of the cases after security refactorings being applied. The resulting p-value of the Wilcoxon signed-rank test is $1.21$x$10^{-10}$. Since the p-value is below the significance level of $0.05$, it is fair to state that \emph{security refactorings have a negative impact in the maintainability of open-source software}.

@@

\Sof{@todo: effect size}

@@

The impact of security refactorings on the maintainability of open-source software per group of security flaws is presented in Figure \ref{fig:pat}. The results of the Wilcoxon signed-rank test by pattern returned statistical evidence which supports the maintainability of open-source software decreases for 4 different patterns: Broken Autentication (p = 0.018), Denial-of-Service (p = 0.029), Memory Leak (p = 0.009) and Miscellaneous (p = $3.07$x$10^{-4}$). The results also returned statistical significance that evidence that maintainability is more likely to not suffer differences for open-source software after removing Components with Known Vulnerabilities (p = $7.96$x$10^{-4}$) and fixing Cross-Site Scripting Vulnerabilities (p = 0.001). Injection and Cross-Site Request Forgery produced more cases where the refactorings had a negative impact in the maintainability. However, the results obtained for these patterns are not statistically significant.

For the Broken Authentication pattern, 55.3\% of the refactorings (21) had a negative impact in the maintainability, 28.95\% (11) improved maintainability and 15.8\% (6) of the changes did not add any impact in the maintainability of open-source software.

%    neg  pos  nul
% ml   41   28   11
% injec   32   31   26
% xss   27   24   63
% misc   84   62   49
% dos   19   12    9
% csrf   17    9    4
% auth   21   11    6
% ucwkv    3    1   17

%        neg       pos       nul
% ml  0.512500  0.350000  0.137500
% injec  0.359551  0.348315  0.292135
% xss  0.236842  0.210526  0.552632
% misc  0.430769  0.317949  0.251282
% dos  0.475000  0.300000  0.225000
% csrf  0.566667  0.300000  0.133333
% auth  0.552632  0.289474  0.157895
% ucwkv  0.142857  0.047619  0.809524
